Exploring dimensions of biodiversity in Japanese ferns

### 2020-07-14 presentations/bsa_2020-07-27/index.Rmd
Update slides
- add references

@@

- *rbcL* sequences from Japanese specimens (Ebihara and Nitta 2019)

@@

- Infer phylogeny with IQ-TREE (Nguyen et al. 2015)

- Date with 26 fossil calibration points (Testo and Sundue 2016) using treePL (Smith and O'Meara 2012)

@@

- `r nrow(trait_summary)` morphological traits mostly used for ID (Ebihara and Nitta 2019)

@@

```{r richness, out.width = "120%"}
# Fern richness
# - map
a <- ggplot(ses_div_ferns_spatial, aes(fill = richness)) +
  geom_sf(color = "transparent") +
  scale_fill_scico(palette = "lajolla") + 
  labs(fill = "No. taxa") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme_pp() +
  theme(
    legend.title = element_text(size = 20/.pt),
    legend.text = element_text(size = 16/.pt),
    legend.justification=c(0,1), legend.position=c(0,1)
  ) +
  ylim(ja_lat_min, ja_lat_max)

@@

@@

.footnote[Shimizu 2014]

@@

>>>>

```{r, load_refs, include=FALSE, cache=FALSE}
library(RefManageR)
BibOptions(
  ignore.case = TRUE,
  check.entries = FALSE, 
  style = "markdown"
)
bib <- ReadBib(here::here("presentations/bsa_2020-07-27/refs.bib"), check = FALSE)
```

@@

- *rbcL* sequences from Japanese specimens `r AutoCite(bib, "Ebihara2019b")`

@@

- Infer phylogeny with IQ-TREE `r AutoCite(bib, "Nguyen2015")`

- Date with 26 fossil calibration points `r AutoCite(bib, "Testo2016a")` using treePL `r AutoCite(bib, "Smith2012")`

@@

- `r nrow(trait_summary)` morphological traits mostly used for ID `r AutoCite(bib, "Ebihara2019b")`

@@

```{r richness, out.width = "130%"}
# Fern richness
# - map
a <- ggplot(ses_div_ferns_spatial, aes(fill = richness)) +
  geom_sf(color = "transparent") +
  scale_fill_scico(palette = "lajolla") + 
  labs(fill = "No. taxa") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme_pp() +
  theme(
    legend.title = element_text(size = 20/.pt),
    legend.text = element_text(size = 16/.pt),
    legend.justification=c(0,1), legend.position=c(0,1)
  ) +
  ylim(ja_lat_min, ja_lat_max)

@@

---
## Classify bioregions using clustering

.middle[
<img src="images/daru_2017.png" alt="drawing" height="400"/>
]

(can also use taxonomic distances)

.footnote[`r Citet(bib, "Daru2017")`]

@@

.footnote[`r Citet(bib, "shimizu_process_2014")`]

@@

---
## References

.small[
```{r, results='asis', echo = FALSE, warning = FALSE}
PrintBibliography(bib, start = 1, end = 5)
```
]

---
## References

.small[
```{r, results='asis', echo = FALSE, warning = FALSE}
PrintBibliography(bib, start = 6, end = 10)
```
]
